CommonMind Consortium: DLPFC

### 2020-09-16 combined_analysis/combine_all_DLPFC.Rmd
bug fixes

### Voom trend plots
```{r plot.voom, fig.height=5, fig.width=10}
fig1 = plot_voom(vobj.lst[[1]]) + ggtitle(names(vobj.lst)[1])
fig2 = plot_voom(vobj.lst[[2]]) + ggtitle(names(vobj.lst)[2])
plot_grid( fig1, fig2, nrow=1) 
```

@@

```{r check.correlation}
ngenes = 300
C1 = cor(t(residuals.lst[[1]][1:ngenes,]))
C2 = cor(t(residuals.lst[[2]][1:ngenes,]))

>>>>

### Voom trend plots
```{r plot.voom, fig.height=5, fig.width=10}
fig1 = plot_voom(vobj.lst[[1]]) + ggtitle(names(vobj.lst)[1])
fig2 = plot_voom(vobj.lst[[2]]) + ggtitle(names(vobj.lst)[2])
plot_grid( fig1, fig2, nrow=1)

df = lapply( names(vobj.lst), function(key){
  data.frame(Cohort = key,  vobj.lst[[key]]$voom.line)
  })
df = do.call(rbind, df)

ggplot(df, aes(x, y, color=Cohort)) + theme_bw(15) + theme(aspect.ratio=1, plot.title = element_text(hjust = 0.5)) + geom_line(size=1.2) + xlab(bquote(log[2](count + 0.5))) + ylab(expression( sqrt("standard deviation"))) + ggtitle("Compare voom trends") + ylim(0, max(df$y)) + scale_color_manual(name="Status", values=c("#3758ba", "#33e65c")) + guides(color = guide_legend(override.aes = list(size = 1))) 
```

@@

```{r check.correlation, eval=FALSE}
ngenes = 300
C1 = cor(t(residuals.lst[[1]][1:ngenes,]))
C2 = cor(t(residuals.lst[[2]][1:ngenes,]))
